---
title: "Homework 1"
author: E. Brennan Bollman
output: github_document
---

This is my solution to homework 1.

```{r}
library(tidyverse)
```


## Problem 1

##### Step 1: Create a date frame with the specified elements.

```{r dataframe_creation}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
prob1_df
```

##### Step 2: Take the mean of each variable in my prob1_df data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

Note: can take mean of numbers and logical vectors, but not character or factor vectors. The logical vector mean uses false=0 and true=1 to calculate a mean. This makes sense!

##### Step 3: Pull each prob1_df variables with as.numeric function to evaluate conversion to numbers.

```{r convert_numeric, eval=FALSE}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

Note: when using as.numeric function, can convert factor to number, but this does not work with character vectors. Because this factor variable has 3 levels, R converts it to numbers 1,2,3. R seems to think characters are really not translatable to numbers. 

##### Step 4: practice manipulations, converting logical vector to numeric or factor and multiplications.

```{r logical_vec_manipulations}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```

Note: the second transformation did not produce valid result, because cannot multiply a categorical variable such as factor. But converting vector into factor, and then that result into a number, did allow for multiplication by my random sample numbers. 

## Problem 2

##### Step 1: load and describe penguins dataset.

```{r penguins data, results='hide'}
data("penguins", package = "palmerpenguins")
penguins
summary(penguins)
```

This is a dataset describing `r n_distinct(penguins$species)` species of penguins known as `r unique(penguins$species)`. The data was collected on `r n_distinct(penguins$island)` islands: `r unique(penguins$island)`. Observations were collected on `r nrow(penguins)` penguins for `r ncol(penguins)` variables between the years `r range(penguins$year)[1]` and `r range(penguins$year)[2]`.

The mean flipper length of all penguins was `r mean(penguins$flipper_length_mm, na.rm = TRUE)`mm. The mean bill length of all penguins was `r mean(penguins$bill_length_mm, na.rm = TRUE)`mm.
