---
title: "Homework 1"
author: E. Brennan Bollman
output: github_document
---

This is my solution to homework 1.

```{r}
library(tidyverse)
```


## Problem 1

Create a date frame with the specified elements.

```{r dataframe creation}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
prob1_df
```

Take the mean of each variable in my prob1_df data frame.

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

Note: can take mean of numbers and logical vectors, but not character or factor vectors.

Pull each prob1_df variables with as.numeric function to evaluate conversion to numbers.

```{r}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

Note: when using as.numeric function, can convert factor to number, but this does not work with character vectors.



## Problem 2

